%************************************************
\addtocontents{toc}{\cftpagenumbersoff{part}}
\addcontentsline{toc}{part}{CHAPTER}
\chapter{INTRODUCTION}\label{ch:introduction}
%************************************************
This template for \LaTeX\ is designed to make formatting your thesis as painless as possible.
\section*{Organization}
\addcontentsline{toc}{section}{Organization}
A very important factor for successful thesis writing is the
organization of the material. This template suggests a structure as
the following:
\begin{itemize}
\item\texttt{Chapters/} is where all the ``real'' content goes in
separate files such as \texttt{Chapter01.tex} etc.
\item\texttt{FrontBackMatter/} is where all the stuff goes that
surrounds the ``real'' content, such as the acknowledgments,
dedication, etc.
\item\texttt{gfx/} is where you put all the graphics you use in
the thesis. Maybe they should be organized into subfolders
depending on the chapter they are used in, if you have a lot of
graphics.
\item\texttt{Bibliography.bib}: the Bib\TeX\ database to organize
all the references you might want to cite.
\item\texttt{ClassicThesis.tex}: the main file of your thesis
where all gets bundled together.
\item\texttt{classicthesis-config.tex}: a central place to load all
nifty packages that are used. In there, you can also activate
backrefs in order to have information in the bibliography about
where a source was cited in the text (\ie, the page number).
\emph{Make your changes and adjustments here.}
You also adjust the title of your thesis, your name, and all
similar information here.
\end{itemize}
In total, this should get you started in no time.
\section*{Citations}
\addcontentsline{toc}{section}{Citations}
In-text citations are fairly straightforward:
\begin{enumerate}
    \item Standard citation. \citep[][p. 123]{bringhurst:2002}
    \item According to Donald Knuth \citeyearpar{knuth:1976}, the "C language rocks". (p. 12)
\end{enumerate}
\subsection*{test subsection}
\addcontentsline{toc}{subsection}{test subsection}
some extra text here
